HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-16 paper/main.tex
ondrej's comments and fixes

% UCCA Motivation
UCCA is a natural candidate for defining a semantic
MT evaluation measure for a number of reasons. 
First, it defines a coarse-grained and intuitive set of categories,
and consequently can be reliably annotated by non-experts, after as little as two hours
of training \cite{marinotti2014}.
Second, UCCA is a cross-linguistically applicable scheme, seeking to represent what is shared between languages,
by building on linguistic typological theory, and specifically on ``Basic Linguistic Theory''
\cite{Dixon:10a,Dixon:10b,Dixon:12}, one of the most widely used frameworks for linguistic description.
Indeed, UCCA's cross-linguistic applicability has been demonstrated through its
application to annotation in English, French, German and Czech\oa{Did we do experiments on Czech?}. 
Third, the scheme has been shown to be semantically stable
in translation: UCCA annotations of translated text usually contain the same set of relationships
\cite{sulem2015conceptual}. This is an indication that the scheme reflects
a common layer of representation that in a correct translation
is mostly shared between the translation and the source. 
We note that that verbal argument structures are less stable in this sense, as a verbal
argument structure may be translated or paraphrased to a nominal or adjectival
argument structure, and are thus less suitable as a basis for a semantic measure.
For example, ``after he graduated, Tom moved to NYC''
conveys a similar meaning to ``after graduation, Tom moved to NYC''.

>>>>

% UCCA Motivation
UCCA is a natural candidate for defining a semantic
MT evaluation measure for a number of reasons. 
First, it defines a coarse-grained and intuitive set of categories,
and consequently can be reliably annotated by non-experts, after as little as two hours
of training \cite{marinotti2014}.
Second, UCCA is a cross-linguistically applicable scheme, seeking to represent what is shared between languages,
by building on linguistic typological theory, and specifically on ``Basic Linguistic Theory''
\cite{Dixon:10a,Dixon:10b,Dixon:12}, one of the most widely used frameworks for linguistic description.
%Indeed, UCCA's cross-linguistic applicability has been demonstrated through its
%application to annotation in English, French, German and Czech\oa{Did we do experiments on Czech?}. 
The cross-linguistic applicability of UCCA has been tested in annotations of
English, French, German and Czech.
Third, the scheme has been shown to be semantically stable
in translation: UCCA annotations of translated text usually contain the same set of relationships
\cite{sulem2015conceptual}. This is an indication that the scheme reflects
a common layer of representation that in a correct translation
is mostly shared between the translation and the source. 
We note that verbal argument structures are less stable in this sense, as a verbal
argument structure may be translated or paraphrased to a nominal or adjectival
argument structure, and are thus less suitable as a basis for a semantic measure.
For example, ``after he graduated, Tom moved to NYC''
conveys a similar meaning to ``after graduation, Tom moved to NYC''.
